\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex

%\clearpage

\section{Reviewer 1's Comments}

\textit{This paper discusses an autonomous object manipulation algorithm using a soft planar grasping manipulator.}

\subsection{Contribution Discussion}
\textit{Several major issues with the paper hold it back. First, the contribution of the paper seems very minor. A considerable amount of the paper is already covered in the work from [12-14], which involves the design of the robot, the recipe to create the robot, and the whole-arm motion planning. The contribution of this work is the grasping algorithm itself, which is a preplanned sequence of robot curvatures. In light of the whole arm motion planner in [12], this contribution seems minor when adding in a (circular) object.  The algorithm itself is implemented as a state-machine method, and with 4 or 5 states and seems trivial. Only one experimental test is performed to demonstrate the algorithm, and no quantitative error metrics are provided.}
We thank the reviewer for pointing out that the contribution is not clear. The contribution of this paper is an autonomous system for object pick-and-place manipulation that can handle objects of unknown geometry using only soft components to build the manipulator. The gripper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space. We revised the introduction section to make the main contribution clear. We also adjusted the text to highlight the extensive experiments. 

@@

We thank the reviewer for pointing out that the contribution is not clear. The contribution of this paper is an autonomous system for object pick-and-place manipulation that can handle objects of unknown geometry using only soft components to build the manipulator. The gripper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space. We revised the introduction section to make the main contribution clear. We also adjusted the text to highlight the extensive experiments. 
%
\textit{For these reasons and especially for the minor contribution that this manuscript offers, I cannot recommend publication as a journal paper in SoRo. The contribution seems better suited for a conference paper submission.}
We believe that the contribution of successfully and repeatedly performing object manipulation using a fully soft, multiple degree of freedom arm is a novel capability. Our feasibility study opens many avenues for soft robotic manipulation. We revised the conclusion section to better articulate these ideas. 
\subsection{Motion-Capture}
\textit{With a motion-capture system, the problem becomes entirely well-defined.
However, soft robotics are specifically designed to work in confined or constrained environments where constraints and obstacles are unknown, with often no line of sight. Discuss how one might actually implement this without a motion-capture system that picks up the entire configuration of the robot manipulator.
Why does soft robotics systems need to specifically be designed for confined or constrained environments only? How is the use of motion capture systems a well-defined problem and how is it such especially in conjunction with soft robotics? Have others done it before, do you have a reference on this?}
We thank the reviewer for this observation.
We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9].
\subsection{Suitable contactless/constrained motion?}
\textit{Section 1.1 Last paragraph: “was only suitable for contactless motion” implies that your proposed method solved motion when the robot is constrained by the environment, but it is rather about gripping objects.}
The sentence was confusing, we clarified the manuscript.
\subsection{Contribution 1}
\textit{Section 1.2 Contribution 1 seems entirely described in [12] and [13]. Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects (as discussed in [21]).}
Contribution 1 is different than the contributions listed in references [12] and [13]. Reference [12] only presents a 6 segment soft arm that can move on a plane, not interaction or manipulation capabilities with objects are shown. The paper deals with the changing body shape of the soft arm when moving it around on a plane. Reference [13] discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work. In this manuscript, we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations. We made clarifications to the contributions sections accordingly.
\subsection{System Overview Figure}
\textit{Section 2. System overview, Figure 2: The image is difficult to see and in its current form, and information of the physical frame surrounding the robot seems unnecessary.}
Thank you for this comment. We moved the labels on the figure. Also, we added to the paper why the physical frame is important to have a mobile presentation platform that can keep the system together, hold the tracking cameras rigidly in place, and does not require recalibration of the tracking cameras. 
\subsection{Fabrication Steps Detailing}
\textit{Section 3.1-3.2 These sections are completely described in [13] and comes off as a recipe to make the manipulator, which is the contribution of [13], and therefore should not be reproduced in the main text. Figure 4 and Table 1. Pulled from [13] seem unnecessary. Furthermore Table 1 does not fit the column.}
Reference 13 includes some description of the fabrication steps, mainly to depict the more generic pleated fabrication process.  The process described in that paper is not complete to allow the reader to reproduce this particular manipulation system. We added further clarification to the text. We also fixed the Table 1 formatting.
\subsection{Motion Tracker}
\textit{Section 4.2 par 1., Which motion tracker was used?}
We used the commercially available The OptiTrack Flex 3 System by Natural Point, Inc. We revised the text to add this information.
\subsection{Optimization Equation}
\textit{Section 4.2 The optimization equation, as I eventually found hidden in Algorithm 1, is difficult to understand: what are parameters v.s. variables, and what is R in the objective function? I suggest writing the equation in the text in full.}
The weights are set by the matrix $\mathbf{R}$. The variables to optimize for are $\phi$ and $\kappa$. All parameters are introduced as inputs to the algorithm. We revised the manuscript to clarify this point and make it easier to find the optimization equation. 
\subsection{Algorithm Difference}
\textit{I also find it difficult to see exactly the difference between the algorithm presented here and the one in [12]. While grasping is indeed is one objective, that seems to be realized by a curvature objective.}

### 2015-10-12 conclusion.tex
two comments left for reviewer 1

The fabrication approach presented has potential to generalize beyond just the fabrication of a gripper.
The new approach is advantageous because it allows for arbitrary designs of internal fluidic cavities and the casting of a homogeneous soft segment. It removes the need for laminating several separately casted parts together.
Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.
x
The results presented in this paper suggest that despite their extreme compliance, soft robots are capable of repeatable object manipulation while simultaneously providing inherently safe interactions with their environment.
The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
We demonstrated the ability of an entirely soft manipulator to autonomously grasp an object, which leads to many potential applications.
In a manufacturing setting, this could resemble a soft robot executing tasks requiring high dexterity when handling delicate objects.
In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.

>>>>

The fabrication approach presented has potential to generalize beyond just the fabrication of a gripper.
The new approach is advantageous because it allows for arbitrary designs of internal fluidic cavities and the casting of a homogeneous soft segment. It removes the need for laminating several separately casted parts together.
Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.

The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
\rkk{The ability to successfully and repeatedly perform object manipulation using a fully soft, multiple degree of freedom arm suggests} that despite their extreme compliance, soft robots are capable of \rkk{reliable and robust} object manipulation while simultaneously providing inherently safe interactions with the environment.
We \rkk{also} demonstrated the \rkk{manipulator's} ability to autonomously grasp an object, which leads to many potential applications \rkk{for full soft robotic manipulation}.
\rkk{In a manufacturing setting, this could resemble a soft robot stretched widely to pick up objects situated at various locations.}
In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
\rkk{To foster those assumptions, future work could investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
Integrating proprioceptive sensing within a multi-segment soft actuator will further improve the use of these manipualtors in occluded environments.}

### 2015-10-12 experimental_results.tex
two comments left for reviewer 1

\subsection{Experimental Insights and Limitations}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper. A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. In that case, the control loop can not function properly until the occlusion disappears. Proprioceptive sensors within the segments can solve this issue. A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

>>>>

\subsection{Experimental Insights and Limitations}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary. The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper. A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner. The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values. The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
In that case, the control loop can not function properly until the occlusion disappears. 
The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
For example, proprioceptive sensors within the segments could solve this issue partially. 
A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

### 2015-10-12 introduction.tex
two comments left for reviewer 1

%More generally, the literature has several examples of soft pneumatic elastomer robots. 
%Many of these robots use open-loop controllers. 
%There are soft fluid-powered rolling robots \cite{correll2010soft, onal2011soft, marchese2011soft}. 
%Also, there are soft-bodied robotic fish powered by pneumatics \cite{marchese2014autonomous} and hydraulics \cite{katzschmann2014hydraulic}. 
%There are soft legged pneumatic walkers \cite{shepherd2011multigait, tolley2014resilient}, explosive jumpers \cite{shepherd2013using}, and 
More recently, Marchese et al. demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free space \cite{marchese2014design} and in confined spaces \cite{marchese2014whole}. Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
The work presented in this paper builds on top of this system and expands its capabilities.
The previous version was only suitable for contactless motions in space, that would be suitable for mere inspection.
The work presented here is capable of autonomous object manipulation on a plane. 
Furthermore, this work shows that combining two different soft actuator types can leverage the strength of each and together achieve a more complicated task of manipulating objects.
The control of the arm is improved from the previous version by using a more robust vision tracking approach. 
Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment. 
Also, many trial runs were needed to arrive at the various final positions in the maze.
%, so the previous system was no repeatable and robust.

\subsection{Contributions}
This work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
We} do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
We provide in this work the following contribution to soft robotics:
\begin{itemize}
  \item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
  \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
  \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
  %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning.} 
\end{itemize}

>>>>

%More generally, the literature has several examples of soft pneumatic elastomer robots. 
%Many of these robots use open-loop controllers. 
%There are soft fluid-powered rolling robots \cite{correll2010soft, onal2011soft, marchese2011soft}. 
%Also, there are soft-bodied robotic fish powered by pneumatics \cite{marchese2014autonomous} and hydraulics \cite{katzschmann2014hydraulic}. 
%There are soft legged pneumatic walkers \cite{shepherd2011multigait, tolley2014resilient}, explosive jumpers \cite{shepherd2013using}, and 
More recently, Marchese et al. demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free space \cite{marchese2014design} and in confined spaces \cite{marchese2014whole}. Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
The work presented in this work builds on top \rkk{of the previous} system and expands its capabilities \rkk{to do actual manipulation}.
The previous version \rkk{was only suitable for moving a soft manipulator through a constrained environment without object interaction or manipulation.
That system is only suitable for inspection tasks}.
The work presented here is capable of autonomous object manipulation on a plane. 
Furthermore, this work shows that combining two different soft actuator types can leverage the strength of each and together achieve a more complicated task of manipulating objects.
The control of the arm is improved from the previous version by using a more robust vision tracking approach. 
Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment. 
Also, previously many trials were needed to successfully arrive at a final position.

\subsection{Contributions}
This work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
We} do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
We provide in this work the following contribution to soft robotics:
\begin{itemize}
  \item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
  \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
  \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
  %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of various delicate objects without requiring force sensing or accurate positioning.} 
\end{itemize}

### 2015-10-12 processing_control.tex
two comments left for reviewer 1

\begin{algorithm}[!htbp]
\begin{small}
  \SetAlgoLined\DontPrintSemicolon
  \KwIn{
  $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ \rkk{measured manipulator} configuration at start \;
  $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
  $x_o$, $y_o$, $r_o$ $\gets$ object center coordinates and radius \;
  $N$ $\gets$ number of manipulator segments}
  \SetKwFunction{planGrasp}{planGrasp}
  \SetKwFunction{findOptimalConfig}{findOptimalConfig}
  \SetKwFunction{forwKin}{forwKin}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\planGrasp{}}{
  $\mathbf{w}_t \gets \forwKin \left( \boldsymbol{\kappa}_{\textrm{meas}}, \, \mathbf{L}_{\textrm{meas}}, \, N, \, L_N \right)$. \;
  $d_1 \gets \| \left[ x_o, \, y_o \right]^{\textrm{T}} \, - \, \mathbf{w}_t \|$. \;
  $d_2 \gets d_1 - r_o - g_{\textrm{off}}$. \;
  $numMoves \gets \lfloor \frac{d_2}{\Delta d} \rfloor$. \;
  $i$ = 0. \;
  \Repeat{$i$ = $numMoves$}{
    $i$ = $i \, + \, 1$ \;
    $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
  }
  \KwRet{$\boldsymbol{\kappa}_i^* \quad \forall i \, = 1.. numMoves$} \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\findOptimalConfig{$r_a$}}{
  $\begin{aligned}
    & \boldsymbol{\kappa}^* \, \gets \, \underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}
    & & \mathbf{R} \, \left( \boldsymbol{\kappa} \, - \, \boldsymbol{\kappa}_{\textrm{off}} \right)^2. \\
    & \text{subject to}
    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r \, \cos{\phi} \\ y_o \, + \, r \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
    & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
    & & & \mathbf{w}_t - \mathbf{w}_{\textrm{off}}\left(r_o, \, \phi \right) - \mathbf{f} \, = \, \mathbf{0}. \\
    & & & \kappa_{n}^{\text{min}} \leq \kappa_n \leq \kappa_{n}^{\text{max}} \quad \forall \, n = 1 \, .. \,N. \\
    \end{aligned}$ \;
  \KwRet{$\boldsymbol{\kappa}^*$} \; }
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\forwKin{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$, $s$ }}{
  \KwIn{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$ the segment of interest index, $s$ the arc length along the indexed segment}
  \eIf{$i = 0$}{
        $\theta_{i}(0) \gets \theta_0(0)$. \;
        $x_{i}(0) \gets 0$.\;
        $y_{i}(0) \gets 0$.\; }
    {
        $\left[ x_{i}(0), \, y_{i}(0), \, \theta_{i}(0) \right] \gets \forwKin \left(\boldsymbol{\kappa}, \, \mathbf{L}, \, i-1, \, L_{i-1} \right)$.\;
    }
    $\theta \gets \theta_{i}(0) + k_i s$. \;
    $x \gets x_{i}(0) + \frac{\sin{\theta}}{k_i} - \frac{\sin{\theta_{i}(0)}}{k_i}$. \;
    $y \gets y_{i}(0) - \frac{\cos{\theta}}{k_i} + \frac{\cos{\theta_{i}(0)}}{k_i}$. \;
  \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
  \caption{Grasp Object Planner}
  \label{alg:planGrasp}
\end{small}

@@

The procedure \rkk{\texttt{planGrasp()} in Algorithm \ref{alg:planGrasp}} first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
The minimal tip transit distance $d_2$ is calculated by \rkk{considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$.} 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure.

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.} The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.

>>>>

\begin{algorithm}[!htbp]
\begin{small}
  \SetAlgoLined\DontPrintSemicolon
  \KwIn{
  $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ \rkk{measured manipulator} configuration at start \;
  $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
  $x_o$, $y_o$, $r_o$ $\gets$ object center coordinates and radius \;
  $N$ $\gets$ number of manipulator segments}
  \SetKwFunction{planGrasp}{planGrasp}
  \SetKwFunction{findOptimalConfig}{findOptimalConfig}
  \SetKwFunction{forwKin}{forwKin}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\planGrasp{}}{
  $\mathbf{w}_t \gets \forwKin \left( \boldsymbol{\kappa}_{\textrm{meas}}, \, \mathbf{L}_{\textrm{meas}}, \, N, \, L_N \right)$. \;
  $d_1 \gets \| \left[ x_o, \, y_o \right]^{\textrm{T}} \, - \, \mathbf{w}_t \|$. \;
  $d_2 \gets d_1 - r_o - g_{\textrm{off}}$. \;
  $numMoves \gets \lfloor \frac{d_2}{\Delta d} \rfloor$. \;
  $i$ = 0. \;
  \Repeat{$i$ = $numMoves$}{
    $i$ = $i \, + \, 1$ \;
    $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
  }
  \KwRet{$\boldsymbol{\kappa}_i^* \quad \forall i \, = 1.. numMoves$} \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\findOptimalConfig{$r_{a_i}$}}{
  $\begin{aligned}
    & \boldsymbol{\kappa}^* \, \gets \, \underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}
    & & \mathbf{R} \, \left( \boldsymbol{\kappa} \, - \, \boldsymbol{\kappa}_{\textrm{off}} \right)^2. \\
    & \text{subject to}
    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r_{a_i} \, \cos{\phi} \\ y_o \, + \, r_{a_i} \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
    & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
    & & & \mathbf{w}_t - \mathbf{w}_{\textrm{off}}\left(r_o, \, \phi \right) - \mathbf{f} \, = \, \mathbf{0}. \\
    & & & \kappa_{n}^{\text{min}} \leq \kappa_n \leq \kappa_{n}^{\text{max}} \quad \forall \, n = 1 \, .. \,N. \\
    \end{aligned}$ \;
  \KwRet{$\boldsymbol{\kappa}^*$} \; }
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\forwKin{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$, $s$ }}{
  \KwIn{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$ the segment of interest index, $s$ the arc length along the indexed segment}
  \eIf{$i = 0$}{
        $\theta_{i}(0) \gets \theta_0(0)$. \;
        $x_{i}(0) \gets 0$.\;
        $y_{i}(0) \gets 0$.\; }
    {
        $\left[ x_{i}(0), \, y_{i}(0), \, \theta_{i}(0) \right] \gets \forwKin \left(\boldsymbol{\kappa}, \, \mathbf{L}, \, i-1, \, L_{i-1} \right)$.\;
    }
    $\theta \gets \theta_{i}(0) + k_i s$. \;
    $x \gets x_{i}(0) + \frac{\sin{\theta}}{k_i} - \frac{\sin{\theta_{i}(0)}}{k_i}$. \;
    $y \gets y_{i}(0) - \frac{\cos{\theta}}{k_i} + \frac{\cos{\theta_{i}(0)}}{k_i}$. \;
  \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
  \caption{Grasp Object Planner}
  \label{alg:planGrasp}
\end{small}

@@

The procedure \rkk{\texttt{planGrasp()} in Algorithm \ref{alg:planGrasp}} first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
The minimal tip transit distance $d_2$ is calculated by \rkk{considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$.} 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found \rkk{by using the optimization equation and constraints described in procedure} \texttt{findOptimalConfig($r_{a_i}$)} \rkk{of Algorithm \ref{alg:planGrasp}}.

\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
\rkk{The weights are set by the matrix $\mathbf{R}$.}
\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.
